---
title: Package documentation
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{vignette-package.Rmd}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
output: rmarkdown::html_vignette
author: Stefan Böhringer <r-packages@s-boehringer.org>
packageName: package
file: vignette-package.Rmd
---

# Purpose of the package

This package is meant to allow the development of ad-hoc packages in a couple of minutes. All that is needed is a single R `list` that defines project properties and is typically 20-30 lines long. Here is an example:

```{r}
packageDefinition = list(
	name = 'pkg-minimal',
	description = list(
			title = 'Minimal R-package created with `package`',
			author = 'Stefan Böhringer <r-packages@s-boehringer.org>',
			description = 'This appears in the package-documentaion, the markdown of the git-repository and in the package details.',
			depends = c(),
			suggests = c(),
			license = 'LGPL',
			news = "0.1-0   Initial release"
	)
);
```

The description key contains a list with information that goes into the `DESCRIPTION` file of the R-package. Apart from this `list`, the file (or another one) should contain the functions you want to put into the package. For example:

```{r}
#' Subject yourself to a message
#' 
#' This function will subject yourself to a message
#' 
#' @author Stefan Böhringer, \email{r-packages@@s-boehringer.org}
#' @examples
#' 
#' myLittlePony()
#'
#' @export myLittlePony
myLittlePony = function() {
	print('this is pateta');
}
```

The documentation is handled via package `roxygen2`, please consult the package documentation. In the example above, the function is exported using the `roxygen2` directive `@export`.

# Git use

The package definition can be amended with a `git` section like so:

```{r}
packageDefinition = list(
	name = 'pkg-minimal',
	description = list(
			title = 'Minimal R-package created with `package`',
			author = 'Stefan Böhringer <r-packages@s-boehringer.org>',
			description = 'This appears in the package-documentaion, the markdown of the git-repository and in the package details.',
			depends = c(),
			suggests = c(),
			license = 'LGPL',
			news = "0.1-0   Initial release"
	),
	git = list(
		readme = '## Installation\n```{r}\nlibrary(devtools);\ninstall_github("githubuser/pkg-minimal")\n```\n',
		push = F,
		pushOnNewVersion = T,
		remote = 'https://github.com/githubuser/pkg-minimal.git'
	)
);
```

`readme` is a character string containing the content of the README file in markdown format. It will be literally written to the file `README.md` in the main folder of the package and is displayed on the homepage of the respository by sites such as github.
`push` is a boolean to indicate whether `createPackage` should automatically push the local source tree. `pushOnNewVersion` restricts pusing to the creation of new versions (see next section).
`remote` is the URL of the remote git server to be pushed to.

# Creating Releases

Releases can be created through the news section of the package definition. If you use git and add a line for a new release, a git-tag with this version number is added to the repository. On github, this leads to the creation of a new release (i.e. tarball/zip for download). In the following example version `0.2-0` is created.

```{r}
packageDefinition = list(
	name = 'pkg-minimal',
	description = list(
			title = 'Minimal R-package created with `package`',
			author = 'Stefan Böhringer <r-packages@s-boehringer.org>',
			description = 'This appears in the package-documentaion, the markdown of the git-repository and in the package details.',
			depends = c(),
			suggests = c(),
			license = 'LGPL',
			news = "0.2-0  Release 0.2-0 was created by adding this line.\n0.1-0   Initial release"
	)
);
```

# Supporting files

Supporing files are installed in subfolder `Rscripts` of the `inst` folder of the package. A character vector with path names can be supplied. All elements are copied recursively to the `inst` subfolder, taking the last path component as file/directory name in `inst`. For example:

```{r}
packageDefinition = list(
	name = 'pkg-minimal',
	instFiles = list(Rscripts = 'Dev/pkg-minimal.R')
	#...
);
```

In the example above, the file `pkg-minimal.R` will be copied to the `inst` folder. These files can be accessed using the `system.file` function as documented in the general R-package creation documentation.


# Vignettes

Vignettes can be written in R-markdown. A vignette entry in the list indicates all files to be included.

```{r}
packageDefinition = list(
	name = 'pkg-minimal',
	description = list(
			title = 'Minimal R-package created with `package`',
			vignettes = "vignettes/vignette-package.Rmd"
			# ...
	)
);
```

Compiled files are copied to the `doc` subfolder of the package. The creation of markdown files (`.md`) is enforced. These can be used to create wiki-pages on popular code hosting sites (`gitlab`, `github`).

