---
title: Package documentation
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Package documentation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
keep_md: TRUE
author: Stefan Böhringer <r-packages@s-boehringer.org>
---

# Purpose of the package

This package is meant to allow the development of ad-hoc packages in a couple of minutes. All that is needed is a single R `list` that defines project properties and is typically 20-30 lines long. Here is an exmaple:

```{r}
packageDefinition = list(
	name = 'pkg-minimal',
	description = list(
			title = 'Minimal R-package created with `package`',
			author = 'Stefan Böhringer <r-packages@s-boehringer.org>',
			description = 'This appears in the package-documentaion, the markdown of the git-repository and in the package details.',
			depends = c(),
			suggests = c(),
			license = 'LGPL',
			news = "0.1-0   Initial release"
	)
);
```

The description key contains a list with information that goes into the `DESCRIPTION` file of the R-package. Apart from this the file (or another one) should contain the functions you want to put into the package. For example:

```{r}
#' Subject yourself to a message
#' 
#' This function will subject yourself to a message [no escape]
#' 
#' @aliases myLittlePony
#' @section Important details: \itemize{
#' \item Be prepared, as in: \code{f0 =
#' f1 = function(){42}; parallelize(f0); parallelize(f1);}
#' \item Be extra prepared
#' }
#' @author Stefan Böhringer, \email{r-packages@@s-boehringer.org}
#' @examples
#' 
#' myLittlePony()
#'
#' @export myLittlePony
myLittlePony = function() {
	print('this is pateta');
}
```

